Presentation For Laura

### 2017-11-15 Laura_pres.Rmd
adding some more stuff

- Based on PCA on correlation matrix of ranked institutional data
- Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
_ Three categories of PhD-granting institutions: R1 to R3

@@

## Densities of Our Scores

```{r, message = FALSE, warning = FALSE}
CCScores_r_cov_predicted <- as.data.frame(lavaan::predict(lavaan_sem_r_cov))
plot(density(CCScores_r_cov_predicted$Overall))
```

>>>>

- Based on PCA on correlation matrix of ranked institutional data
- Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
- Three categories of PhD-granting institutions: R1 to R3

@@

## Densities of Our Scores
Distribution was bimodal - schools were grouped into two groups
```{r, message = FALSE, warning = FALSE}
CCScores_r_cov_predicted <- as.data.frame(lavaan::predict(lavaan_sem_r_cov))
plot(density(CCScores_r_cov_predicted$Overall))
library(beanplot)
beanplot(CCScores_r_cov_predicted$Overall, col = c("blue",'orange'), method = "jitter")
title("SEM Classifications")
```
